### 2022-07-23 paper/localpsf.tex
small changes to paper, adding a true velocity plot which has a colorbar the same size as the true parameter and also including an image which is notCropped in case we would like to edit it in the future
adding Glen reference to paper and bib

\begin{subequations}\label{Stokeseqn}
	\begin{align}
	-\nabla\cdot\bm{\sigma}_{\bm{u}}
	&=\rho\bm{g}\,\,\,\text{ in }\icedomain, \label{Stokeseqn:1}\\
	\nabla\cdot\bm{u}
	&=0\,\,\,\,\,\,\text{ in }\icedomain, \label{Stokeseqn:2}\\
	\bm{\sigma}_{\bm{u}}\bm{n}
	&=\bm{0}\,\,\,\,\,\,\text{ on }\Gamma_{t}, \label{Stokeseqn:3}\\
	\bm{u}\cdot\bm{n} =0 \quad\text{and}\quad \bm{T}\left(\bm{\sigma}_{\bm{u}}\bm{n}+\exp\left(\basalfriction\right)\bm{u}\right)
	&=\bm{0}\,\,\,\,\,\,\text{ on }\Gamma_{b},\label{Stokeseqn:4} \\
	\left(\bm{\sigma}_{\bm{u}}\bm{n}+\mu\bm{u}\right)&=\bm{0}\,\,\,\,\,\,\text{ on }\Gamma_{l}.\label{Stokeseqn:5}	
	\end{align}
\end{subequations}
The solution to these equations is the tuple $(\bm{u}, p)$, where $\bm{u}$ is the ice flow velocity, and $p$ is the pressure. Here, $\basalfriction$ is the unknown logarithmic
basal sliding parameter field which is defined on the $2D$ surface $\Gamma_b$. The quantity $\rho\bm{g}$ is the body force density due to gravity, $\bm{n}$ is the outward normal and $\bm{T}$ is the tangential projection operator that restricts a vector field to its tangential component along the boundary. 
We employ Glen's flow law
(CITE GLEN) %\cite{glen1955},
which is a constitutive law for ice that relates the stress
tensor $\bm{\sigma}_{\bm{u}}$ and the strain rate tensor
$\bm{\dot{\varepsilon}}_{\bm{u}}= \frac{1}{2}\left(
\bm{\nabla}\bm{u}+\bm{\nabla}\bm{u}^{\top} \right)$, $\bm{\sigma}_{\bm{u}}= 2\eta
\bm{\dot{\varepsilon}}_{\bm{u}} -\bm{I}p$, where $\eta=\frac{1}{2}A^{-1}$ is the effective viscosity, $\bm{I}$ is the unit matrix,
and $A$ is a flow rate factor. Glen's exponent has been chosen $n=1$, which provides for a linear Stokes model. Note that while the PDE is linear, the parameter-to-solution map, $\basalfriction \mapsto (\bm{u}, p)$, is nonlinear.

@@

\begin{figure}[H]
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.243]{mtrue_withColorBar.png}
		\caption{True $\basalfriction$.}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.18]{trueVelocity_glyphs_withColorBar.png}
		\caption{True $\bm{u}$.}
	\end{subfigure}
	\caption{True logarithmic basal sliding parameter $\basalfriction$ (left) and true velocity $\bm{u}$ (right). In the right plot, arrows indicate the direction of $\bm{u}$ and color indicates the magnitude of $\bm{u}$.}
\end{figure}

>>>>

\begin{subequations}\label{Stokeseqn}
	\begin{align}
	-\nabla\cdot\bm{\sigma}_{\bm{u}}
	&=\rho\bm{g}\,\,\,\text{ in }\icedomain, \label{Stokeseqn:1}\\
	\nabla\cdot\bm{u}
	&=0\,\,\,\,\,\,\text{ in }\icedomain, \label{Stokeseqn:2}\\
	\bm{\sigma}_{\bm{u}}\bm{n}
	&=\bm{0}\,\,\,\,\,\,\text{ on }\Gamma_{t}, \label{Stokeseqn:3}\\
	\bm{u}\cdot\bm{n} =0 \quad\text{and}\quad \bm{T}\left(\bm{\sigma}_{\bm{u}}\bm{n}+\exp\left(\basalfriction\right)\bm{u}\right)
	&=\bm{0}\,\,\,\,\,\,\text{ on }\Gamma_{b},\label{Stokeseqn:4} \\
	\left(\bm{\sigma}_{\bm{u}}\bm{n}+\mu\bm{u}\right)&=\bm{0}\,\,\,\,\,\,\text{ on }\Gamma_{l}.\label{Stokeseqn:5}	
	\end{align}
\end{subequations}
The solution to these equations is the tuple $(\bm{u}, p)$, where $\bm{u}$ is the ice flow velocity, and $p$ is the pressure. Here, $\basalfriction$ is the unknown logarithmic
basal sliding parameter field which is defined on the $2D$ surface $\Gamma_b$. The quantity $\rho\bm{g}$ is the body force density due to gravity, $\bm{n}$ is the outward normal and $\bm{T}$ is the tangential projection operator that restricts a vector field to its tangential component along the boundary. 
We employ Glen's flow law \cite{Glen1955},
which is a constitutive law for ice that relates the stress
tensor $\bm{\sigma}_{\bm{u}}$ and the strain rate tensor
$\bm{\dot{\varepsilon}}_{\bm{u}}= \frac{1}{2}\left(
\bm{\nabla}\bm{u}+\bm{\nabla}\bm{u}^{\top} \right)$, $\bm{\sigma}_{\bm{u}}= 2\eta
\bm{\dot{\varepsilon}}_{\bm{u}} -\bm{I}p$, where $\eta=\frac{1}{2}A^{-1}$ is the effective viscosity, $\bm{I}$ is the unit matrix,
and $A$ is a flow rate factor. Glen's exponent has been chosen $n=1$, which provides for a linear Stokes model. Note that while the PDE is linear, the parameter-to-solution map, $\basalfriction \mapsto (\bm{u}, p)$, is nonlinear.

@@

\begin{figure}[H]
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.243]{mtrue_withColorBar.png}
		\caption{True $\basalfriction$.}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\includegraphics[scale=0.243]{trueVelocity2_glyphs.png}
		\caption{True $\bm{u}$.}
	\end{subfigure}
	\caption{True logarithmic basal sliding parameter $\basalfriction$ (left) and true velocity $\bm{u}$ (right). In the right plot, arrows indicate the direction of $\bm{u}$ and color indicates the magnitude of $\bm{u}$.}
\end{figure}
